### 2021-07-31 paper/localpsf.tex
boundary extension written okish

\subsubsection{Greedy ellipsoid packing algorithm}
\label{sec:greedy_point_selection}

Now that we have estimates of the supports of the functions $\phi_x$, we use these estimates, combined with a greedy ellipsoid packing algorithm to choose sets of sample points, $S_b$. These sample points will be used in Section \ref{sec:get_impulse_response} to form Dirac combs, which are then used to compute impulse responses of $\mathcal{A}$. We start with a finite set of candidate points $P$. To build a batch of sample points, $S_b$, first we initialize $S_b$ as an empty set. Then we select the point $p \in P$ that is the farthest away from all points in previous sample point batches. That is, $p$ is a maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
Once $p$ is selected, we remove $p$ from $P$. If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. Recall that $E_p$ and $E_q$ are ellipsoids associated with points $p$ and $q$, respectively, as defined in \eqref{eq:support_ellipsoid}. This process repeats until there are no more points in $P$.  This is detailed in Algorithm \ref{alg:point_choice}. We determine whether $E_p \cap E_q = \{\}$ using the fast ellipsoid intersection test described in Appendix \ref{sec:fast_ellipsoid_intersection_test}.

@@

While $\varphi_{x_i}$ may be undefined at a point $z$, often there is a sample point $x_j$ that is near $x_i$, but further away from the boundary than $x_i$, such that $\varphi_{x_j}$ is well defined at $z$. To address boundary artifacts, we fill in missing/undefined portions of convolution kernels using information from other convolution kernels associated with the $k$ nearest sample points. Kernels associated with nearer sample points are given precedence over kernels associated with farther away sample points. After the convolution kernel has been extended using information from neighboring convolution kernels, it is then further extended by zero as needed.

Let $x_{n_1}, x_{n_2}, \dots, x_{n_k}$ be the $k$ nearest sample points to $x_i$, ordered by nearness, including $x_i$ itself. That is, $x_{n_1}=x_i$ (the point itself), $x_{n_2}$ is the nearest sample point to $x_i$ other than $x_i$ itself, $x_{n_3}$ is the second nearest sample point to $x_i$ other than $x_i$ itself, and so on. Also, recall that in computations that the functions $\varphi_{x_i}$ are stored on regular rectilinear grids. To extend $\varphi_{x_i}$, first we form an expanded regular rectilinear grid that has the same grid spacing as the grid used for $\varphi_{x_i}$, but is large enough to contain the boxes associated with all of the neighbor kernels $\varphi_{x_{n_1}}, \varphi_{x_{n_2}}, \dots, \varphi_{x_{n_k}}$. We initialize an extended convolution kernel, $\varphi_{x_i}^E$, to zero on this expanded grid. Then we interpolate the functions $\varphi_{x_{n_j}}$ onto this expanded grid one at a time in reverse order. That is, first we interpolate the kernel, $\varphi_{x_{n_k}}$, associated with the furthest point from $x_i$ onto the grid, then the kernel, $\varphi_{x_{n_{k-1}}}$, associated with the second furthest point, and so on until we reach the original kernel $\varphi_{x_{n_1}} = \varphi_{x_i}$. At each step, we overwrite existing values of $\varphi_{x_i}^E$ with new values from the kernel currently being interpolated, except when the new value of $\varphi_{x_{n_j}}$ is undefined (``NaN''). At gridpoints where the kernel being interpolated is undefined, we leave $\varphi_{x_i}^E$ unchanged. In this way, we fill in undefined values of $\varphi_{x_i}$ with values from successively further and further away kernels. This process is illustrated in Figure FIG. To avoid notational clutter, and since we will henceforth only work with the extended kernel, $\varphi_{x_i}^E$, in the remainder of this paper the symbol $\varphi_{x_i}$ refers to $\varphi_{x_i}^E$.

>>>>

\subsubsection{Greedy ellipsoid packing}
\label{sec:greedy_point_selection}

Now that we have estimates of the supports of the functions $\phi_x$, we use these estimates, combined with a greedy ellipsoid packing algorithm, to choose sets of sample points, $S_b$. These sample points will be used in Section \ref{sec:get_impulse_response} to form Dirac combs, which are then used to compute impulse responses of $\mathcal{A}$. We start with a finite set of candidate points $P$. To build a batch of sample points, $S_b$, first we initialize $S_b$ as an empty set. Then we select the point $p \in P$ that is the farthest away from all points in previous sample point batches. That is, $p$ is a maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
Once $p$ is selected, we remove $p$ from $P$. If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. Recall that $E_p$ and $E_q$ are ellipsoids associated with points $p$ and $q$, respectively, as defined in \eqref{eq:support_ellipsoid}. This process repeats until there are no more points in $P$.  This is detailed in Algorithm \ref{alg:point_choice}. We determine whether $E_p \cap E_q = \{\}$ using the fast ellipsoid intersection test described in Appendix \ref{sec:fast_ellipsoid_intersection_test}.

@@

While $\varphi_{x_i}$ may be undefined at a point $z$, often there is a sample point $x_j$ that is near $x_i$, but further away from the boundary than $x_i$, such that $\varphi_{x_j}$ is well defined at $z$. To address boundary artifacts, we fill in missing/undefined portions of convolution kernels using information from other convolution kernels associated with the $k$ nearest sample points. Kernels associated with nearer sample points are given precedence over kernels associated with farther away sample points. After the convolution kernel has been extended using information from neighboring convolution kernels, it is then further extended by zero.

In detail, let $x_{n_1}, x_{n_2}, \dots, x_{n_k}$ be the $k$ nearest sample points to $x_i$, ordered by nearness, including $x_i$ itself. That is, $x_{n_1}=x_i$ (the point itself), $x_{n_2}$ is the nearest sample point to $x_i$ other than $x_i$ itself, $x_{n_3}$ is the second nearest sample point to $x_i$ other than $x_i$ itself, and so on. Also, recall that in computations that the functions $\varphi_{x_i}$ are stored on regular rectilinear grids. To extend $\varphi_{x_i}$, first we form an expanded regular rectilinear grid that has the same grid spacing as the grid used for $\varphi_{x_i}$, and contains that grid as a subgrid, but is large enough to contain the boxes associated with all of the neighbor kernels $\varphi_{x_{n_1}}, \varphi_{x_{n_2}}, \dots, \varphi_{x_{n_k}}$. We initialize an extended convolution kernel, $\varphi_{x_i}^E$, to zero on this expanded grid. Then we interpolate the functions $\varphi_{x_{n_j}}$ onto this expanded grid one at a time in reverse order. That is, first we interpolate the $\varphi_{x_{n_k}}$ onto the grid, then the kernel $\varphi_{x_{n_{k-1}}}$, and so on until we reach the original kernel $\varphi_{x_{n_1}} = \varphi_{x_i}$. At each step, we overwrite existing values of $\varphi_{x_i}^E$ with new values from the kernel currently being interpolated, except when the new value of $\varphi_{x_{n_j}}$ is undefined (``NaN''). At gridpoints where the kernel being interpolated is undefined, we leave $\varphi_{x_i}^E$ unchanged. In this way, we fill in undefined values of $\varphi_{x_i}$ with values from successively further and further away kernels. This process is illustrated in Figure FIG. To avoid notational clutter, and since we will henceforth only work with the extended kernel, $\varphi_{x_i}^E$, in the remainder of this paper the symbol $\varphi_{x_i}$ refers to $\varphi_{x_i}^E$.
